Adaptability of ecophysiological traits define how plant lineages make a living in shaded environments 

### 2019-03-13 manuscript/manuscript.Rmd
data table and a vs n plots

```{r speciestable, echo=FALSE,warning=FALSE, message=FALSE}}
library(pixiedust)
speciestab <- read.csv("raw_data/species_list.csv")

@@

\
**Table 2**.

@@

>>>>

```{r, speciestable, echo=FALSE,warning=FALSE, message=FALSE}
library(pixiedust)
speciestab <- read.csv("raw_data/species_list.csv")

@@

\
**Table 2**. Pooled ecophysiological traits for different plant lineages in open light and closed habitats.

```{r, datatable, echo=FALSE,warning=FALSE, message=FALSE}
traitstab <- read.csv("manuscript/pooled_data.csv")
physymb <- '\u03D5'

dust(traitstab)%>%
  sprinkle_colnames("Plant Lineage", "Canopy", "*A*~n~","*g*~s~","Foliar N",
                    "Foliar P", "C:N", "N:P", "SD", physymb, "*R*~d~", "LCP") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

```{r nitro, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs, warning=FALSE, message=FALSE}
source("master_scripts/bivariate_plots.R")
```  
**Figure 6**. Postive relationship between photosynthesis and foliar nitrogen content exists for angiosperms and fern species in open light habitat, but not in shade habitats
